Assessing the Reliability of JavaScript Engines by Leveraging Diversity

### 2018-08-01 paper/paper.tex
minor fixed in table

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team since April,
    2018. The analysis of warnings was not uninterrupted.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Seed \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}}
    & \Fix{x} & LO & WebKit \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}}
    & \Fix{x} & HI & WebKit \\
    3  & 4/14 & radamsa & JavascriptCore  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & \Fix{x}  & HI & WebKit    \\
    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}}
    & \Fix{x} & HI & JerryScript   \\
    9  & 4/29 & radamsa & JavascriptCore  & New  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & \Fix{x}  & HI  & JerryScript\\
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076}}
    & \Fix{x} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & \Fix{x} &  & \\
    11 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & \Fix{x} & LO & Mozilla \\
    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128}}
    & \Fix{x} & HI & JerryScript \\
    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182}}
    & \Fix{x} & HI & V8\\
    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & \Fix{x} & HI & Webkit\\
    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & \Fix{x} & HI & JerryScript\\
    20 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & \Fix{x} & HI & JerryScript\\
    21 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443}}
    & \Fix{x} & HI & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Seed \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}}
    & \Fix{x} & LO & WebKit \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}}
    & \Fix{x} & HI & WebKit \\
    3  & 4/14 & radamsa & JavascriptCore  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & \Fix{x}  & HI & WebKit    \\
    4  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}}
    & \Fix{x} & HI & JerryScript   \\
    5  & 4/29 & radamsa & JavascriptCore  & New  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & \Fix{x}  & HI  & JerryScript\\
    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076}}
    & \Fix{x} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & \Fix{x} &  & \\
    7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & \Fix{x} & LO & Mozilla \\
    8 & 5/10 & radamsa & Chakra & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128}}
    & \Fix{x} & HI & JerryScript \\
    9 & 5/17 & radamsa & Chakra & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182}}
    & \Fix{x} & HI & V8\\
    10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & \Fix{x} & HI & Webkit\\
    11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & \Fix{x} & HI & JerryScript\\
    12 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & \Fix{x} & HI & JerryScript\\
    13 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443}}
    & \Fix{x} & HI & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}
